Katana: A Userland Toolchain-Oriented Hotpatching System

### 2010-06-22 doc/katana.tex
updated documentation

% Created 2010-06-20 Sun 22:23
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

@@

   Katana aims to be much less invasive than other hot-patching system
   and require minimal work to be used with any project. It does,
   however, have some requirements.\\
   Required CFLAGS:
\begin{itemize}
\item -g
\end{itemize}
   Recommended CFLAGS:
\begin{itemize}
\item -ffunction-sections
\item -fdata-sections
\end{itemize}
   Recommended LDFLAGS:
\begin{itemize}
\item --emit-relocs
\end{itemize}
\subsection{To Generate a Patch}
\label{sec-6.2}

>>>>

% Created 2010-06-20 Sun 23:06
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

@@

    Katana aims to be much less invasive than other hot-patching system
    and require minimal work to be used with any project. It does,
    however, have some requirements.\\
\subsubsection{Source Code Practices}
\label{sec-6.1.1}

    Katana does not look at the source code, therefore unlike several
    other hotpatching systems, it does not require any annotation in
    the source code. There are, however, some best practices to
    follow.
\begin{itemize}
\item Avoid the use of \texttt{void*} at least for global variables (since
      Katana does not currently patch local variables, preferring to
      wait until any functions using changed variables are no longer
      on the stack). Since it is typeless and opaque, it is very hard
      to analyze and patch.
\item Avoid unnamed types. i.e., instead of \texttt{typedef struct \{...\} Foo;}
      use \texttt{typedef struct Foo\_ \{...\} Foo;}.
\item Avoid accessing structure members by offsets instead of by the
      member names. As long as you keep all the code where you do this
      up to date, it should not be a problem, but katana cannot detect
      when you do this.
\end{itemize}
\subsubsection{Compilation/Linking}
\label{sec-6.1.2}

    Required CFLAGS:
\begin{itemize}
\item -g
\end{itemize}
    Recommended CFLAGS:
\begin{itemize}
\item -ffunction-sections
\item -fdata-sections
\end{itemize}
    Recommended LDFLAGS:
\begin{itemize}
\item --emit-relocs
\end{itemize}
\subsection{To Generate a Patch}
\label{sec-6.2}
